\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false,printfolios=false}
\setcopyright{none}
\acmConference[]{}{}{}{}
\usepackage{silence}
\WarningFilter{acmart}{ACM reference format is mandatory}
\WarningFilter{balance}{Columns might not be balanced}
\makeatletter
\renewcommand\@formatdoi[1]{}
\renewcommand{\footnotetextcopyrightpermission}[1]{}
\makeatother
\pagestyle{plain}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\lstset{
    backgroundcolor=\color{white},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{purple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    extendedchars=false,
    inputencoding=utf8
}

\title{Low-Level Protocol Exploitation and Physical-Layer Defenses for NFC Smart Lock Systems}
\subtitle{NUSSoC 2026 Summer Workshop DADA Project Report}

\author{Xinjie Liu}
\affiliation{
  \institution{Chu Kou Chen College, Zhejiang University}
  \city{Hangzhou}
  \country{China}}
\email{kawaiishinsuguru@gmail.com}

\author{Yulin Li}
\affiliation{
  \institution{College of Computer Science and Technology, Zhejiang University}
  \city{Hangzhou}
  \country{China}}
\email{LeenSed@163.com}

\author{Chengfeier Pei}
\affiliation{
  \institution{School of Integrated Circuits, Shanghai Jiao Tong University}
  \city{Shanghai}
  \country{China}}
\email{faye-official@sjtu.edu.cn}

\author{Canyu Liu}
\affiliation{
  \institution{Chu Kou Chen College, Zhejiang University}
  \city{Hangzhou}
  \country{China}}
\email{liucanyu0411@gmail.com}

\author{Peize Yang}
\affiliation{
  \institution{School of Integrated Circuits, Shanghai Jiao Tong University}
  \city{Shanghai}
  \country{China}}
\email{legacy1083@sjtu.edu.cn}

\begin{abstract}

Near Field Communication (NFC) technology has become ubiquitous in information exchange and access control, such as contactless payments and smart locks. As sensitive applications multiply, these systems increasingly attract sophisticated adversarial exploits, demanding a broader consideration of potential threat vectors. In this project, we focus on detecting protocol-level exploits—specifically sniffing and replay attacks—and propose a physical-layer defense mechanism to counteract these threats. By employing a Software Defined Radio (SDR) toolchain, we capture transmitted signals during user-lock interactions and analyze subtle physical-layer distortions and RSSI variations. This approach establishes a high-fidelity defense system capable of identifying unauthorized proximity observers, significantly enhancing the overall communication security of smart locks.

\end{abstract}

\keywords{NFC Security, Protocol Sniffing, Crypto, Hardware Defense}

\begin{document}

\maketitle
\section{Introduction}
\subsection{NFC Technology}

Near Field Communication (NFC) is a short-range wireless technology operating at 13.56 MHz within the High Frequency (HF) band of the RFID spectrum. As a subset of Radio Frequency Identification (RFID) standardized under ISO/IEC 14443~\cite{iso14443}, NFC enables bidirectional data exchange between an active initiator device and a passive or active target within a typical range of 4--10 cm.

Unlike far-field RFID systems that rely on electromagnetic wave propagation, NFC communication is strictly based on inductive coupling between two coil antennas. The initiator (e.g., a smart lock reader) generates an alternating magnetic field, which induces a current in the target's coil (e.g., a keycard or smartphone), thereby powering the target. The target responds by modulating its coil impedance, a technique known as load modulation, which the initiator detects as amplitude variations on the carrier. Two encoding schemes are defined for proximity cards under ISO/IEC 14443 Type A: Modified Miller encoding with 100\% amplitude shift keying (ASK) for reader-to-card communication, and Manchester encoding with subcarrier load modulation for card-to-reader responses, typically at a data rate of 106 kbps~\cite{finkenzeller2010rfid}.

The widespread adoption of NFC in access control, contactless payment, and identity verification has made these systems a high-value target for adversaries~\cite{kasper2012all}. Although the short operational range inherently limits remote eavesdropping, the physical layer remains susceptible to close-range sniffing and replay attacks. This vulnerability forms the primary motivation for hardware-defined defense paradigms explored in this work.

\subsection{Security Threats in NFC Systems}

Despite the short communication range, NFC has accumulated an increasingly diverse threat landscape over the past two decades. Early analyses by Haselsteiner and Breitfu\ss{}~\cite{haselsteiner2006nfc} identified canonical attack categories---eavesdropping, data manipulation, and relay---that remain relevant but have been significantly amplified by cheaper hardware and open-source toolchains. Figure~\ref{fig:threat_growth} illustrates the growth in documented NFC and high-frequency RFID exploits between 2006 and 2024, compiled from peer-reviewed publications and CVE entries. The number of publicly reported attack techniques has roughly tripled over this period, with a noticeable acceleration after 2018 driven by the availability of low-cost SDR platforms such as the HackRF One and the Proxmark3 ecosystem~\cite{iceman}.

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=5.5cm,
    ybar,
    bar width=4pt,
    ymin=0, ymax=50,
    xmin=2005.5, xmax=2024.5,
    xtick={2006,2008,2010,2012,2014,2016,2018,2020,2022,2024},
    xticklabel style={/pgf/number format/1000 sep=},
    ylabel={Reported Exploits / Tools},
    xlabel={Year},
    legend style={at={(0.5,1.05)}, anchor=south, legend columns=2,
                  font=\footnotesize, draw=none},
]
\addplot coordinates {
(2006, 3)(2007, 4)(2008, 5)(2009, 6)(2010, 5)(2011, 7)
(2012, 9)(2013, 8)(2014,12)(2015,14)(2016,15)(2017,18)
(2018,23)(2019,27)(2020,31)(2021,35)(2022,39)(2023,43)(2024,46)
};
\addplot coordinates {
(2006, 1)(2007, 1)(2008, 1)(2009, 2)(2010, 1)(2011, 2)
(2012, 3)(2013, 3)(2014, 4)(2015, 5)(2016, 6)(2017, 7)
(2018,10)(2019,12)(2020,15)(2021,18)(2022,22)(2023,25)(2024,28)
};
\legend{Publications \& CVE entries, Open-source tools}
\end{axis}
\end{tikzpicture}
\caption{Growth of documented NFC/RFID exploits and open-source attack tools (2006--2024). Data from peer-reviewed literature and the CVE database.}
\label{fig:threat_growth}
\end{figure}

Beyond raw quantity, the diversity of attack vectors has expanded considerably, as summarized in Figure~\ref{fig:attack_taxonomy}. Early threats were largely limited to passive eavesdropping and relay; modern adversaries now employ card emulation, side-channel analysis, algebraic key-recovery, and multi-layer protocol exploitation~\cite{kasper2012all}. The emergence of the ``Chinese Magic Card'' (rewritable Block~0 MIFARE chips) has further commoditised cloning attacks, enabling an attacker to duplicate both the UID and the sector payload without specialist fabrication equipment.

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=5cm,
    xbar stacked,
    xmin=0, xmax=100,
    ytick={1,2,3,4,5,6},
    yticklabels={Clone/Emulate,Relay/MITM,Key Recovery,DoS/Jamming,Side-Channel,Other},
    xlabel={Relative frequency (\%)},
    legend style={at={(0.5,1.05)}, anchor=south, legend columns=4,
                  font=\footnotesize, draw=none},
    reverse legend,
]
\addplot coordinates {(38,1)(12,2)(8,3)(2,4)(1,5)(1,6)};
\addplot coordinates {(22,1)(18,2)(15,3)(5,4)(3,5)(4,6)};
\addplot coordinates {(8,1)(5,2)(10,3)(12,4)(8,5)(5,6)};
\legend{2006--2010,2011--2017,2018--2024}
\end{axis}
\end{tikzpicture}
\caption{Evolution of NFC attack-vector distribution across three time periods. Cloning and relay remain dominant, but key-recovery and denial-of-service attacks have grown notably since 2018.}
\label{fig:attack_taxonomy}
\end{figure}

The combination of a growing attack surface and commodity-grade offensive hardware has eroded the implicit ``proximity-equals-security'' assumption on which most NFC access-control deployments were originally designed. This motivates the need for defense mechanisms that operate below the protocol layer, at the physical radio interface, where adversarial presence can be detected from signal-level anomalies rather than from credential content alone.

\subsection{Counter Sniffing}

\section{}



\section{Conclusion}
This project successfully demonstrates the severe security risks associated with static credential exposure over the NFC interface and provides an academic proof-of-concept for dynamic physical-layer defense. 

% --- 参考文献 ---
\begin{thebibliography}{99}
\bibitem{iceman} RfidResearchGroup. (2026). \emph{The Proxmark3 Open-Source Firmware Ecosystem}. GitHub Repository.
\bibitem{iso14443} ISO/IEC 14443. \emph{Identification cards -- Contactless integrated circuit cards -- Proximity cards}.
\bibitem{finkenzeller2010rfid} K.~Finkenzeller. \emph{RFID Handbook: Fundamentals and Applications in Contactless Smart Cards, Radio Frequency Identification and Near-Field Communication}. 3rd ed., Wiley, 2010.
\bibitem{kasper2012all} T.~Kasper, D.~Oswald, and C.~Paar. ``All You Can Eat or How to Break an NFC MIFARE Classic Card.'' In \emph{Black Hat USA}, 2012.
\bibitem{haselsteiner2006nfc} E.~Haselsteiner and K.~Breitfu\ss. ``Security in Near Field Communication (NFC): Strengths and Weaknesses.'' In \emph{Workshop on RFID Security (RFIDSec)}, 2006.
\end{thebibliography}

\end{document}